figures and calculations for global fisheries management

### 2019-01-13 documents/figs-and-calcs.Rmd
prep for turfs
three types of classification up

turf_all <- full_join(projection_turf, turf_all_1, by= c("Country", "SciName"))%>%
  ungroup()%>%
  select(Country, SciName) %>%
  distinct()

@@

all_turfs <- plyr::join(d_turfs, edf_turf, by= c("Country", "SciName", "CatchShare"), type = "full" ) %>%
  distinct()

turfs <- plyr::join(all_turfs, isscaap, by= c("SciName")) %>%
  filter(SciName !="NA")%>%
  filter(SpeciesCat != "NA")

#add the turf data to upside
projection_turfs <- merge(projection_data, turfs, by = c("Country", "SciName", "SpeciesCat", "CatchShare"), all = T)

projection_turfs_mutate <- projection_turfs  %>%
  mutate(MainCat = case_when(
    SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",
    SpeciesCat == 31 | SpeciesCat == 32 | SpeciesCat == 33 | SpeciesCat == 34 | SpeciesCat     == 35 | SpeciesCat == 37 ~ "3",
    SpeciesCat == 42 | SpeciesCat == 43 | SpeciesCat == 44 | SpeciesCat == 45 | SpeciesCat      == 47 ~ "4",
    SpeciesCat == 52 | SpeciesCat == 53 | SpeciesCat ==54 |  SpeciesCat == 55 | SpeciesCat     == 56 | SpeciesCat == 57 | SpeciesCat == 58 ~ "5",
    SpeciesCat == 74 | SpeciesCat == 76 | SpeciesCat == 77 ~ "7"
  ))

@@

#question here, will the filter remove out when year is NA? the turf data doesn't have this resolution; edf does have start date though
join_mutate <- left_join(projection_turfs_mutate, gdp, by = "Country") %>% 
  group_by(IdOrig) %>%
  dplyr::mutate(max_year = max(Year)) %>% 
  filter(max_year== 2012)

join_mutate$MainCat <- factor(join_mutate$MainCat)

downjoin <- caret::downSample(x = select(join_mutate,-CatchShare),
                              y = factor(join_mutate$CatchShare),
                              yname = "CatchShare")
downjoin %>% 
  ggplot(aes(log(MSY),fill = CatchShare)) + 
  geom_density()

@@

bayes_itq_broad_fit <-
  rstanarm::stan_glmer(
    formula = CatchShare ~ gdp_center + (1|MainCat),
    family = "binomial",
    data = downjoin,
    cores = 4
  )

@@

orig_itq_broad_fit <- join_mutate %>% 
  mutate(pred = predict(itq_broad_fit, type = "response", newdata = join_mutate))

@@

aug_itq_broad_fit %>% 
  ggplot(aes(gdp_center, pred, color = MainCat)) + 
  geom_point()

aug_itq_broad_fit %>% 
  ggplot(aes(MainCat, pred)) + 
  geom_boxplot()

catchshare_pred_plot

@@

pROC::ggroc(g) + 
  geom_abline(aes(intercept = 1, slope =  1), color = "red") + 
  labs(x = "")

>>>>

turf_all <- full_join(projection_turf, turf_all_1, by= c("Country", "SciName"))%>%
  ungroup()%>%
  select(Country, SciName) %>%
  distinct() %>% 
  left_join(projection_data %>% select(Country, SciName,IdOrig) %>% unique())

@@

all_turfs <- dplyr::full_join(d_turfs, edf_turf, by= c("Country", "SciName", "CatchShare")) %>%
  distinct()

turfs <-
  dplyr::left_join(all_turfs, unique(isscaap), by = c("SciName")) %>%
  filter(SciName != "NA") %>%
  filter(SpeciesCat != "NA") %>%
  select(-CatchShare) %>%
  mutate(turf = 1,
         Year = 2012)

#add the turf data to upside
projection_turfs <- full_join(projection_data, turfs, by = c("Country", "SciName", "SpeciesCat","Year"), all = T) %>% 
  mutate(turf = ifelse(is.na(turf),0,1)) %>% 
  mutate(CatchShare = ifelse(turf == 1,2, CatchShare))

check <- projection_turfs %>% 
  filter(turf == 1)

projection_turfs %>% 
  group_by(CatchShare) %>% 
  count()

main_cat <- str_extract_all(projection_turfs$SpeciesCat,"^\\d", simplify = TRUE)

projection_turfs$MainCat <- main_cat

# projection_turfs <- projection_turfs  %>%
#   mutate(MainCat = case_when(
#     SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",
#     SpeciesCat == 31 | SpeciesCat == 32 | SpeciesCat == 33 | SpeciesCat == 34 | SpeciesCat     == 35 | SpeciesCat == 37 ~ "3",
#     SpeciesCat == 42 | SpeciesCat == 43 | SpeciesCat == 44 | SpeciesCat == 45 | SpeciesCat      == 47 ~ "4",
#     SpeciesCat == 52 | SpeciesCat == 53 | SpeciesCat ==54 |  SpeciesCat == 55 | SpeciesCat     == 56 | SpeciesCat == 57 | SpeciesCat == 58 ~ "5",
#     SpeciesCat == 74 | SpeciesCat == 76 | SpeciesCat == 77 ~ "7"
#   ))

@@

#question here, will the filter remove out when year is NA? the turf data doesn't have this resolution; edf does have start date though
catch_shares <- left_join(projection_turfs, gdp, by = "Country") %>% 
  group_by(IdOrig) %>%
  dplyr::mutate(max_year = max(Year)) %>% 
  filter(max_year== 2012,
         CatchShare %in% c(0,1),
         !is.na(gdp_center),
         !is.na(MainCat),
         Year == max_year) %>% 
  ungroup() %>% 
  mutate(MainCat = factor(MainCat))

catch_shares_and_turfs <- left_join(projection_turfs, gdp, by = "Country") %>% 
  group_by(IdOrig) %>%
  dplyr::mutate(max_year = max(Year)) %>% 
  filter(max_year== 2012,
         CatchShare %in% c(1,2),
          !is.na(gdp_center),
         Year == max_year) %>% 
  ungroup() %>% 
  mutate(MainCat = factor(MainCat)) %>% 
  mutate(CatchShare = CatchShare - 1)

everything <- left_join(projection_turfs, gdp, by = "Country") %>% 
  group_by(IdOrig) %>%
  dplyr::mutate(max_year = max(Year)) %>% 
  filter(max_year== 2012,
         Year == max_year,
                   !is.na(gdp_center)) %>% 
  ungroup() %>% 
  mutate(MainCat = factor(MainCat))

```{r is-catch-share}

downjoin <- caret::upSample(x = select(catch_shares,-CatchShare),
                              y = factor(catch_shares$CatchShare),
                              yname = "CatchShare")

@@

@@

orig_itq_broad_fit <- catch_shares %>% 
  ungroup() %>% 
  mutate(pred = predict(itq_broad_fit, type = "response", newdata = catch_shares))

@@

@@

catch_share_roc <- pROC::ggroc(g) + 
  geom_abline(aes(intercept = 1, slope =  1), color = "red") + 
  labs(x = "")

```{r turf-v-cs}

upjoin <-
  caret::upSample(
    x = select(catch_shares_and_turfs, -CatchShare),
    y = factor(catch_shares_and_turfs$CatchShare),
    yname = "CatchShare"
  )

cs_or_turf_fit <-
  glm(
    formula = CatchShare ~ gdp_center + SpeciesCatName,
    family = "binomial",
    data = upjoin
  )

summary(cs_or_turf_fit)

aug_fit <- broom::augment(cs_or_turf_fit) %>% 
  mutate(pred = predict(cs_or_turf_fit, type = "response"))

orig_cs_or_turf_fit <- catch_shares_and_turfs %>%
  ungroup() %>%
  mutate(pred = predict(cs_or_turf_fit, type = "response", newdata = catch_shares_and_turfs))

  cs_or_turf_pred_plot <- orig_cs_or_turf_fit %>%
  ggplot(aes(pred, CatchShare == 1, fill = CatchShare == 1)) +
  ggridges::geom_density_ridges(show.legend = FALSE, alpha = 0.75) +
  geom_vline(aes(xintercept = 0.5), linetype = 2, color = "red") +
  labs(y = "Is TURF?",
       x = "Probability of TURF",
       caption = "Classified as TURF if p>0.5") +
  scale_x_continuous(limits = c(0, 1), expand = c(0, .01))

g <- pROC::roc(CatchShare ~ pred, data = orig_cs_or_turf_fit)

catch_share_turf_roc <- pROC::ggroc(g) + 
  geom_abline(aes(intercept = 1, slope =  1), color = "red") + 
  labs(x = "")

```{r multinom}

upjoin <-
  caret::upSample(
    x = select(everything, -CatchShare),
    y = factor(everything$CatchShare),
    yname = "CatchShare"
  )

everything_fit <-
  multinom(
    formula = CatchShare ~ gdp_center + SpeciesCatName,
    family = "binomial",
    data = upjoin
  )

orig_everything_fit <- everything %>%
  ungroup() %>%
  mutate(pred = predict(everything_fit, type = "class", newdata = everything))

confusion_matrix <- orig_everything_fit %>% 
  group_by(CatchShare,pred) %>% 
  summarise(n = length(MSY), tmsy = sum(MSY, na.rm = T)) %>% 
  filter(!is.na(pred)) %>% 
  ungroup() %>% 
  # group_by(CatchShare) %>% 
  mutate(pn = n / sum(n),
         pmsy = tmsy / sum(tmsy)) %>% 
  mutate(pnn = scales::percent(pn, accuracy = 1),
         pnm = scales::percent(pmsy, accuracy = 1)) %>% 
  ungroup() %>% 
  mutate(CatchShare = fct_recode(factor(CatchShare),"Catch Share" = "1", "Non-RBFM" = "0", "TURF" = "2")) %>% 
  mutate(pred = fct_recode(factor(pred),"Catch Share" = "1", "Non-RBFM" = "0", "TURF" = "2"))

confusion_matrix %>% 
  ggplot() + 
  geom_tile(aes(pred,CatchShare,fill = pn),color = "black",alpha = 0.25) +
  geom_text(aes(pred, CatchShare, label = pnn)) +
  scale_fill_viridis_c() + 
  scale_x_discrete(position = "top", name = "Predicted Management") + 
  labs(y = "Observed Management")

confusion_matrix %>% 
  ggplot() + 
  geom_tile(aes(pred,CatchShare,fill = pmsy),color = "black",alpha = 0.25) +
  geom_text(aes(pred, CatchShare, label = pnm)) +
  scale_fill_viridis_c() + 
  scale_x_discrete(position = "top", name = "Predicted Management") + 
  labs(y = "Observed Management")
